---
title: "PA1_tempalte"
output: html_document
---
# Reproducible Research: Peer Assessment 1

```{r setup, echo=TRUE}
setwd("C:/DATA/coursera/5-6.Reproducible Research/week 2")
library("knitr", lib.loc="C:/Program Files/R/R-3.3.1/library")
library("ggplot2", lib.loc="C:/Program Files/R/R-3.3.1/library")
library(plyr)
base <- read.table(file="activity.csv", sep=",", dec=",", header=T, stringsAsFactors=F)
head(base)
dim(base)  
summary(base)
```

## Processing the Data

```{r,echo=TRUE}
##выдергивать данные без NA
clean <- base[!is.na(base$steps),]
```

## What is mean total number of steps taken per day?
Calculate the total number of steps taken per day
Make a histogram of the total number of steps taken each day

```{r1, echo=TRUE}
summ <- aggregate(base$steps ~ base$date, FUN=sum, )
colnames(summ)<- c("Date", "Steps")
hist(summ$Steps, breaks=5, xlab="Шаги, шт.",ylab="Количество повторов, шт.", main = "Количество шагов в день")
```

Calculate and report the mean and median of the total number of steps taken per day
```{r3,echo=TRUE}
as.integer(mean(summ$Steps))
as.integer(median(summ$Steps))
```

Calculate the total number of steps per day using dplyr and group by date:
```{r4,echo=TRUE}
interval <- base %>%
  filter(!is.na(steps)) %>%
  group_by(interval) %>%
  summarize(steps = mean(steps))

```

##What is the average daily activity pattern?

```{r5,echo=TRUE}
#какая средняя активность за день
clean <- base[!is.na(base$steps),]
##создать интервал с средним количеством шагов
intervalTable <- ddply(clean, .(interval), summarize, Avg = mean(steps))
 
##Создать график среднего числа шагов в интервале
p <- ggplot(intervalTable, aes(x=interval, y=Avg), xlab = "Интервал", ylab="Среднее количество шагов")
p + geom_point()+xlab("Интервал")+ylab("Среднее количество шагов")+ggtitle("Среднее количество шагов за интервал")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r6,echo=TRUE}
#максимальное количество шагов за интервал
maxSteps <- max(intervalTable$Avg)
 
##Какой интервал содержит максимальное среднее количество шагов
intervalTable[intervalTable$Avg==maxSteps,1]

```
The maximum number of steps for a 5-minute interval was 206 steps.

The 5-minute interval which had the maximum number of steps was the 835 interval.

##Imputing missing values
Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r7,echo=TRUE}
##Количество NA в исходном наборе данных
nrow(base[is.na(base$steps),])

```
## Create the average number of steps per weekday and interval
```{r8,echo=TRUE}
avgTable <- ddply(clean, .(interval, day), summarize, Avg = mean(steps))
## Создать набор данных со всеми NA для замещения
nadata<- base[is.na(base$steps),]
 
## Слияние данных NA c средним недельным интервалом
newdata<-merge(nadata, avgTable, by=c("interval", "day"))
 
## Переупорядочивание данных с подстрокой в том же формате что и исходные данные
newdata2<- newdata[,c(6,4,1,2,5)]
colnames(newdata2)<- c("steps", "date", "interval", "day", "DateTime")
 
##Слияние средних значений из набора данных с NA и без 
mergeData <- rbind(clean, newdata2)
```

##Create sum of steps per date to compare with step 1
Mean of Steps with NA data taken care of
Median of Steps with NA data taken care of
```{r9,echo=TRUE}
##Сумма шагов для каждой даты
summ2 <- aggregate(mergeData$steps ~ mergeData$date, FUN=sum, )
colnames(summ2)<- c("Date", "Steps")
 
## Среднее количество шагов с NA
as.integer(mean(summ2$Steps))
 
## Медиана шагов с данными NA
as.integer(median(summ2$Steps))
```
## Creating the histogram of total steps per day, categorized by data set to show impact
```{r10,echo=TRUE}
## Диаграмма суммарного количества шагов в день
hist(summ2$Steps, breaks=5, xlab="Шаги", main = "Общее количество шагов с NA", col="red")
hist(summ$Steps, breaks=5, xlab="Шаги", main = "Общее количество шагов с NA", col="blue", add=T)
legend("topright", c("Imputed Data", "Non-NA Data"), fill=c("red", "blue") )

```
##Are there differences in activity patterns between weekdays and weekends?
Average Steps per Interval Based on Type of Day
```{r11,echo=TRUE}
mergeData$DayCategory <- ifelse(mergeData$day %in% c("суббота", "воскресенье"), "Weekend", "Weekday")
library(lattice) 
library("lattice", lib.loc="C:/Program Files/R/R-3.3.1/library")
intervalTable2 <- ddply(mergeData, .(interval, DayCategory), summarize, Avg = mean(steps))
xyplot(Avg~interval|DayCategory, data=intervalTable2, type="o",  layout = c(1,2),
       main="Среднее число шагов за дневной интервал", 
       ylab="Среднее число шагов", xlab="Интервал")

```
